---
name: Chris
surname: Lundberg
address: "3072 West 107th Place, Unit C | Westminster, CO 80031"
phone: 720-256-8363
www: deviationstation.io
email: "chris@deviationstation.io"
github: chris-lundberg
linkedin: chris-lundberg
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Data Science Skills
**Communication:** data analysis reports, dashboard design, interactive applications, presentations

**Data Wrangling:** data acquisition (csv, database, API, web scraping), cleaning, and transformation 

**Statistics:** exploratory data analysis, model selection and validation, machine learning, time series analysis, NLP

**Programming Languages:** R, Python, SQL, Java, C

**Tools:** Linux, Git, Apache Airflow, Elasticsearch, Shiny

# Education

```{r}
library(readr)
read_csv("education.csv") %>% 
  detailed_entries(degree, year, institution, location)
```





