---
name: Chris
surname: Lundberg
address: "6347 South Albion Way | Centennial, CO 80121"
phone: 720-256-8363
www: deviationstation.io
email: "chris@deviationstation.io"
github: chris-lundberg
linkedin: chris-lundberg
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Data Science Skills
**Communication:** data analysis reports, dashboard design, interactive applications, presentations

**Data Wrangling:** data acquisition (database, API, web scraping), cleaning, and transformation 

**Statistics:** EDA, time series analysis, machine learning (classification, regression, unsupervised learning)

**Programming Languages:** R (tidyverse, tidymodels, keras), Python (numpy, pandas, scikit-learn), SQL, Java, C

**Tools:** Linux, Git, Apache Airflow, Elasticsearch, Shiny

# Experience

```{r}
library(readr)
read_csv("experience.csv") %>% 
  detailed_entries(title, dates, company, location, accomplishments)
```

# Education

```{r}
read_csv("education.csv") %>% 
  detailed_entries(degree, year, institution, location, experience)
```

# Professional Development
 
**Professional Designations:** CFA charterholder

**Entrepreneur Mentorship:** Rockies Venture Club, Rocky Mountain Microfinance Institute

**Volunteering:** Manning Publications, Reading Partners

**Speaking:** [*What Metrics Matter? A Public Equity Investor's Perspective*](https://github.com/chris-lundberg/measure-what-matters) - [TiE Denver](https://www.tiedenver.org/wp-event/monthly-business-for-breakfast-on-public-market-metrics/)






