---
name: Chris
surname: Lundberg
address: "6347 South Albion Way | Centennial, CO 80121"
phone: 720-256-8363
email: "chris@scaleanalytics.co"
github: chris-lundberg
linkedin: chris-lundberg
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE) 
library(vitae)
library(tidyverse)
```

# Skills and Certifications
**Data Wrangling:** data acquisition (database, API, web scraping), cleaning, and transformation 

**Statistics:** EDA, time series analysis, machine learning (classification, regression, unsupervised learning)

**Programming Languages:** R, Python, SQL, Java, C

**Professional Designations:** CFA charterholder

**Certifications:** AWS Certified Cloud Practitioner, AWS Certified Machine Learning - Specialty

# Experience

```{r}
library(readr)
read_csv("experience.csv") %>% 
  detailed_entries(title, dates, company, location, accomplishments)
```

# Education

```{r}
read_csv("education.csv") %>% 
  detailed_entries(degree, year, institution, location, experience)
```








